---
title: "02 Data Acqusition"
date: "2021-04"
output:
  html_document:
    toc: true
    toc_float: true
    df_print: paged
    collapsed: false
    number_sections: true
    toc_depth: 3
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```

# Data Acquisition

Last compiled: `r Sys.Date()`

## Challenge 1: API

I have decided to access university data listed by country. One can simply enter a country and an output of all possible univeristies and their corresponding websites is generated as an output.

### Load Libraries

```{r}
library(dplyr)
library(httr)
library(glue)
library(rvest)
library(stringr)
library(purrr)
library(tibble)
library(tidyverse)
library(jsonlite)
```

### Write API Function

```{r}
universities_api <- function(country) {
  url <- modify_url(url = "http://universities.hipolabs.com", path = glue("/search?country={country}"))
  resp <- GET(url)
  stop_for_status(resp)
}
```

### Enter Country and Get Data

```{r}
#Argument can be any country. Replace spaces with a plus sign, e.g. in case of United States type "United+States"
resp <- universities_api("Germany")

#get into tibble
uni_tbl <- resp %>% 
  .$content %>% 
  rawToChar() %>% 
  fromJSON()

#reorganize in tibble
output_tbl <- uni_tbl %>% select(name, web_pages) %>% rename(Name = name, Website = web_pages)
```

### Output (First Five Universities)

```{r}
output_tbl %>% head(n = 5)
```

## Challenge 2: Web Scraping

I have decided to scrape the names and prices of all racing bikes from rosebikes.de

### Libraries

All necessary libraries are already loaded.

### Write Scraping Function

```{r}
scrape_data <- function(url) {
  
  #access html file
  html_racing_bikes <- read_html(url)
  
  #get bike names by css
  bike_name  <- html_racing_bikes %>%
    html_nodes(css = ".catalog-category-bikes__title-text") %>%
    html_text()%>% str_replace_all("[\r\n]" , "") %>% 
    enframe(name = "No.", value = "Name")
  
  #get bike prices by css
  bike_price  <- html_racing_bikes %>%
    html_nodes(css = ".catalog-category-bikes__price-title") %>%
    html_text() %>% str_replace_all("[\r\n]" , "") %>% 
    enframe(name = "No.", value = "Price") 
  
  #combine prices and names and surpress output of number
  bike_info <- left_join(bike_name,bike_price) %>% select(-("No."))
}
```

### Enter URL and Output

```{r}
url= "https://www.rosebikes.de/fahrr%C3%A4der/rennrad"
bike_output<-scrape_data(url)
bike_output
```
